Depression and suicidality as costly signals of need

### 2021-04-22 Paper.rmd
Added alternate intro

>>>>

### alternate start

Conflicts of interest are ubiquitous among living things, even among closely related individuals. The result of this is often situations in which one individual benefits greatly from another while providing little benefits or substantial costs in return. In species which rely heavily on cooperation, like our own, this often manifests in substantial outward conflict about levels of investment the harm an individual is inflicting on another.

Both depression and suicide attempts are more common outcomes of these sorts of conflict than is often appreciated by the biomedical approach (Syme and Hagen 2021). With notable exceptions (Kendler; Mazure; Hammen), the biomedical model tends to frame both suicide and depression as a problem with the individual, e.g., as one involving psychiatric disturbance, drug addiction, or stress sensitivity [@wray2011 (changed wording to include depression]. This theoretical approach has made little progress: rates of suicide, which vary widely by country, have remained relatively flat in countries for which there are long-term data, such as the US, UK, Japan, and Sweden [@owidsuicide] (tweak for depression).

## Anthropology of depression and suicide 
Anthropology, in contrast, has long viewed depression and suicide attempts as largely stemming from social problems. Continue from below Durkheim
